A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-09-15 paper/paper.tex
paper: polish
paper: MAJ

\subsection{Augmented semi-simplicial sets}
We consider the category of augmented semi-simplices, which can be written in different ways, up to equivalence. We proceed to describe to combinatorial definition.
\begin{definition}[\DeltaPlus]
  The category of augmented semi-simplices is defined in terms of objects and morphisms:

  \begin{align*}
    \obj(\DeltaPlus) & := \Nat                                                                            \\
    \hom(p, n)       & := \{i_{p + 1}, \ldots, i_n \mid p < i_{p + 1} < i_{p + 2} < \ldots < i_n \leq n\} \\
    f \circ g        & := \text{concatenation of the sequences $f$ and $g$}
  \end{align*}
\end{definition}

@@

\subsection{Semi-cubical sets}
\begin{definition}[\Cube]
  \begin{align*}
    \obj(\Cube) & := \Nat                                                                                                             \\
    \hom(p, n)  & := \{(i_{p + 1}, \epsilon_{p + 1}) \ldots, (i_n, \epsilon_n) \mid p < i_{p + 1} < i_{p + 2} < \ldots < i_n \leq n\} \\
    f \circ g   & := \text{concatenation of the sequences $f$ and $g$}
  \end{align*}
\end{definition}

@@

Here, $\I{n}$ serves the purpose of \sq{n}, but this change will cascade into other definitions. In view of defining a category \CSet, we will restrict the morphisms in \Cube.

Or, in terms of objects and morphisms:

@@

\subsection{Generalization to \texorpdfstring{$\nu$}{nu}}

\begin{table}[H]
  \begin{tabularx}{\linewidth}{p{.2\linewidth}|p{.4\linewidth}|p{.3\linewidth}}
    \toprule
    Value of $\nu$ & 1                     & 2                  \\
    \graymidrule
    Interpretation & Semi-simplicial types & Semi-cubical types \\
    \bottomrule
  \end{tabularx}
\end{table}

>>>>

\subsection{Augmented semi-simplicial sets}
We consider the category of augmented semi-simplices, which can be written in different ways, up to equivalence. Here, we describe the combinatorial definition.

\begin{notation}[Sequences of integers]
  We write $\{i_1, \ldots i_n\}$ for (ordered) sequences of integers. In particular, the empty sequence is written $\{\}$.
\end{notation}

\begin{definition}[\DeltaPlus]
  The category of augmented semi-simplices is defined in terms of objects and morphisms:

  \begin{align*}
    \obj(\DeltaPlus)   & := \Nat                                                                                    \\
    \hom(p, n)         & := \{i_{p + 1}, \ldots, i_n \mid 0 < i_{p + 1} < \ldots < i_n \leq n\}                     \\
    g \circ f          & := \{i_{j_{p + 1}}, \ldots, i_{j_n} \mid j_0 < i_{j_{p + 1}} < \ldots < i_{j_n} \leq j_n\} \\
    \id \in \hom(n, n) & := \{\}                                                                                    \\
  \end{align*}
\end{definition}

@@

\subsection{Semi-cubical sets}
\begin{notation}[Faces of cube]
  We use $\epsilon$ to indicate opposite faces of a cube; it takes values $+$ or $-$.
\end{notation}

\begin{definition}[\Cube]
  \begin{align*}
    \obj(\Cube)        & := \Nat                                                                                                             \\
    \hom(p, n)         & := \{(i_{p + 1}, \epsilon_{p + 1}) \ldots, (i_n, \epsilon_n) \mid p < i_{p + 1} < i_{p + 2} < \ldots < i_n \leq n\} \\
    g \circ f          & :=                                                                                                                  \\
    \id \in \hom(n, n) & := \{\}                                                                                                             \\
  \end{align*}
\end{definition}

@@

@@

\subsection{Generalization to \texorpdfstring{$\nu$}{nu}}
\begin{table}[H]
  \begin{tabularx}{\linewidth}{p{.2\linewidth}|p{.4\linewidth}|p{.3\linewidth}}
    \toprule
    Value of $\nu$ & 1                     & 2                  \\
    \graymidrule
    Interpretation & Semi-simplicial types & Semi-cubical types \\
    \bottomrule
  \end{tabularx}
\end{table}
